Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-18 icmssp-paper/parts/02_02_cryptoimg.tex
Minor changes

\subsection{Intensity Transformations in CryptoImg}
A paper published in 2009 by Ziad, et al. implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. The resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure}

An intensity transformation on a digital image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$. Table \ref{tab:imageoperation_summary} shows common image intensity transformations~\cite{gonzalez_digital_2008}.

% The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization. 
The \textit{CryptoImg} library implemented two types of intensity transformations: image negation and brightness control, which are both linear transformations. In this study,we consider two common non-linear transformations. the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}, seen in Table \ref{tab:imageoperation_summary}.

>>>>

\subsection{Intensity Transformations in CryptoImg}
A paper published in 2009 by Ziad, et al. implements privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The \textit{CryptoImg} library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. The resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/ClientServerModel.png}
    \caption{Architecture used by \textit{CryptoImg}, from \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure}

An intensity transformation on a digital image $R$ can be defined as a function $T$ which is applied to every pixel $r$ in $R$. Table \ref{tab:imageoperation_summary} shows common image intensity transformations~\cite{gonzalez_digital_2008}. 
The \textit{CryptoImg} library implemented two types of intensity transformations: image negation and brightness control, which are both linear transformations. 
In this study, we consider two common non-linear transformations. the logarithm transformation and power-law transformation~\cite{gonzalez_digital_2008}, seen in Table \ref{tab:imageoperation_summary}.

% The \textit{CryptoImg} library implemented the following image processing operations: image negation, brightness adjustment, spatial filters (for noise reduction, edge detection and sharpening), morphological operations, and histogram equalization.

### 2019-03-18 icmssp-paper/parts/02_03_facialrecognition.tex
Minor changes

Traditional facial recognition algorithms rely on detecting salient features in a face image. One of the popular facial recognition algorithms is \textit{eigenfaces}.
% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.

% \subsubsection{Eigenfaces}
Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.

@@

% \subsection{Previous Implementations of Secure Facial Recognition}
Erkin, et al. \cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method. In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the clear.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
\end{figure}

>>>>

Traditional facial recognition algorithms rely on detecting salient features in a face image. Proposed by Matthew Turk and Alex Pentland, the \textit{eigenfaces} method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.
% One of the popular facial recognition algorithms is \textit{eigenfaces}.
% Traditional facial recognition algorithms rely on detecting salient features in a face image. Two of the popular facial recognition algorithms are \textit{eigenfaces} and \textit{Haar cascades}.

% \subsubsection{Eigenfaces}

@@

% \subsection{Previous Implementations of Secure Facial Recognition}
Erkin, et al. \cite{hutchison_privacy-preserving_2009} devised a method to incorporate the use of homomorphic cryptosystems into the eigenfaces method, primarily using the Paillier cryptosystem. In their study, they proposed a two-party system where Alice holds an encrypted image $\left[\Gamma\right]$, while Bob maintains a database of $K$ eigenfaces $\mathbf{u}_1, \ldots, \mathbf{u}_K$, and feature vectors $\Omega_1, \ldots, \Omega_M$ in the plaintext domain.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
    \caption{Diagram of the privacy-preserving facial recognition process, from \cite{hutchison_privacy-preserving_2009}}
\end{figure}
